Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-11-05 edubots_surveys.Rnw
Correcting students' survey

The introduction of new technologies in the classroom, to be successful, involves extra teacher training, devising methods for enhancing student engagment with the new technology and in deed acquiring new skills by both. Some technologies are readily adopted, but others require longer time for full adoption. In most cases, the magnitude of the uptake of the new technology impinges on the collaboration of all the parties using it. Hence, examining the users’ opinions and 
is an important first step in boosting this collaboration and reaping the benefits of the technology.  Recently, a surge in the use of synchronous instant messaging tools in higher education such as WhatsApp, Telegram and Facebook Messenger took place. Some messaging applications have built in chatbots that are able to support a synchronous conversation between the different parties \cite{differ.chat}, while other chatbots are developed as standalone systems and can possibly be attached to a messaging application using an API (Application Program Interface).

@@

 The line of research of which this paper is a part has involved two phases of data collection.
 \begin{itemize}
\item The first phase aimed to collect feedback from students about their actual needs \cite{MoraChatbots2021:anon}. Hence, the objective was to collect information about students’ preferences of tools/applications for chatting and messaging, how they use them in educational context, who do they like to be with in the class messaging groups, and their expectations of the chatbots in terms of assisting them during their learning process. Therefore, two surveys for bachelor and master degree students at the University of Granada (Spain) were designed and answers from more than 250 students were collected. The key findings of the students surveys reveal that they prefer to use messaging applications, such as Telegram or WhatsApp as they are familiar to them. Students also expressed interest in chatbots that can assist them with organizing their course schedules, help them access their assignment grades and facilitate searching for course's resources. 
\item The results of the first phase were fed into the second phase of the study, which focused on teachers’ opinions about using chatbots and messaging applications in classes. This is what is going to be presented in this paper.
\end{itemize}

>>>>

The introduction of new technologies in the classroom involves a combination of teacher training, student enthusiasm and possibly acquiring new skills by both. Some technologies are readily adopted, but others require longer time for full adoption. In most cases, the magnitude of the uptake of the new technology impinges on the collaboration of all the parties using it. Hence, examining the users’ opinions and 
is an important first step in boosting this collaboration and reaping the benefits of the technology.  Recently, a surge in the use of synchronous instant messaging tools in higher education such as WhatsApp, Telegram and Facebook Messenger took place. Some messaging applications have built in chatbots that are able to support a synchronous conversation between the different parties \cite{differ.chat}, while other chatbots are developed as standalone systems and can possibly be attached to a messaging application using an API (Application Program Interface).

@@

 The line of research of which this paper is a part has involved two phases of data collection.
 \begin{itemize}
\item The first phase aimed to collect feedback from students about their actual needs \cite{MoraChatbots2021:anon}. Hence, the objective was to collect information about students’ preferences of tools/applications for chatting and messaging, how they use them in educational context, who do they like to be with in the class messaging groups, and their expectations of the chatbots in terms of assisting them during their learning process. Therefore, two surveys for bachelor and master degree students at the University of Granada (Spain) were designed and answers from more than 250 students were collected. The key findings of the students' surveys reveal that they prefer to use messaging applications, such as Telegram or WhatsApp as they are familiar to them. Students also expressed interest in chatbots that can assist them with organizing their course schedules, help them access their assignment grades and facilitate searching for course's resources. 
\item The results of the first phase were fed into the second phase of the study, which focused on teachers’ opinions about using chatbots and messaging applications in classes. This is what is going to be presented in this paper.
\end{itemize}
